\chapter {Detector Simulation}

\section {Offline Software Overview}

\subsection {G4dyb}

G4dyb is a application program composed of GEANT4.
G4dyb provides many preliminary simulation tasks and could be
the validation of NuWa, the later offline software.
The version control of G4dyb is CVS in the early days and
SVN later. CMT is used to manage the configuration of G4dyb.
The latest version of G4dyb is release ------------, and
G4dyb has been stopped to develop around in the middle of last year(2008).


\subsection {NuWa}

NuWa is the official offline software of Dayabay experiment.
It contains not only the physics simulation engine, but also
other offline programs, including electronic simulation,
trigger simulation, analysis programs, and so forth.

NuWa is a framework, which is different from G4dyb.
A framework-----------------------, ------------------.
It could be realized NuWa is a assembly of many kinds of application program,
e.g. Root, the analysis framework developed by CERN, GEANT4, and so forth.
The framework is based on Gaudi. Gaudi is ----------------------.

NuWa communicates with GEANT4 by GiGa, Gaudi interface to GEANT application-------.
A typical script to control GiGa is Python. The simulation structure scheme is shown below.


(NuWa simulation structure scheme)


The version control of NuWa is SVN and CMT is used to manage
the configuration of NuWa. At the time of writing, the latest
version of NuWa is 1.3.0--------------------------.

The algorithm of NuWa simulation scheme is shown below.


(simulation algorithm scheme of NuWa)





NuWa overview

why NuWa

DataModel AES TES

Gaudi

Giga


\subsubsection {Comparison of NuWa and G4dyb}





\section {Mock Data Challenge}

http://dayabay.ihep.ac.cn/cgi-bin/DocDB/ShowDocument?docid=2602

\section {Basic Distributions of Dayabay and Aberdeen Neutron Detectors}

\section {The Effect of Reflector Position}

\section {The Effect of Optical Property Measurement Uncertainty}
