Opticks is an open source project that accelerates optical photon simulation  
by integrating GPU ray tracing, accessed via the NVIDIA OptiX 7 API, with 
Geant4 based simulations. 
A single NVIDIA Turing GPU, first RTX generation, has been measured to provide optical 
photon simulation speedup factors exceeding 1500 times single threaded Geant4 
with a full JUNO analytic GPU geometry automatically translated from the Geant4 geometry.
%
Optical physics processes of scattering, absorption, scintillator reemission and 
boundary processes are implemented in CUDA programs based on Geant4.
Wavelength-dependent material and surface properties as well as  
inverse cumulative distribution functions for reemission are interleaved into 
GPU textures providing fast interpolated property lookup or wavelength generation.
%

In this work we describe the near complete re-implementation required to adopt 
the entirely new NVIDIA OptiX 7 API, with the implementation now directly CUDA 
based with OptiX usage restricted to providing intersects.  
The new Opticks features a modular many small header
design that provides fine grained testing both on GPU and CPU 
together with large code reductions from CPU/GPU sharing.  
Enhanced modularity has enabled CSG tree generalization to support "list-nodes", 
similar to G4MultiUnion, that improve performance for complex CSG solids.  
In addition support for interference effects on boundaries with multiple thin layers,
such as anti-reflection coatings and photocathodes, using CUDA compatible
transfer matrix method (TMM) calculations of reflectance, transmittance and
absorptance are reported.
